Using Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2020-12-09 thesis/thesis.tex
thesis: Add NGC 2516 results

\pagebreak

@@

This process is explained in more detail in Appendix \ref{chap:feature_selection}.

@@

% TODO: Fix table if figures changes
\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \textbf{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \textbf{$\mu_{\delta}$ $(mas/yr^{-1})$} & \textbf{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr}\tablefootnote{Results have been taken from \protect\citeA[p.~25. Table A.3. Pleiades]{babusiaux2018gaia}} &
        19.997 $\pm$ 0.127 & -45.548 $\pm$ 0.101 & 7.364 $\pm$ 0.005 & 1326 \\
      Clusterix+TOPCAT & 19.98 $\pm$ 1.25 & -45.47 $\pm$ 1.48 & 7.33 $\pm$ 0.21 & 634 \\
      KMeans & 20.25 $\pm$ 35.16 & -38.01 $\pm$ 40.16 & 7.23 $\pm$ 2.35 & 1378 \\
      DEC & 23.67 $\pm$ 38.33 & -46.23 $\pm$ 44.54 & 8.04 $\pm$ 2.59 & 878 \\
      \textbf{DEC (filtered)} & 19.50 $\pm$ 8.59 & -44.23 $\pm$ 8.17 & 7.42 $\pm$ 0.1 & 438 \\
    \end{tabular}
    \caption{Melotte 22. The parameters shown are proper motion in right ascension and declination, parallax and number of stars with their respective deviations.}
    \label{tab:results_melotte_22}
  \end{center}
\end{table}

@@

\pagebreak

@@

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 Clusterix+TOPCAT characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 KMeans characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 DEC characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_pm_filtered_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_filtered_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_filtered_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 DEC (filtered) characterization.}
\end{figure}

\begin{table}[H]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      \# Clusters & 10 \\
      Clustering Layer & $\left[ 50, 50, 40 \right]$ \\
      Kernel Initializer Seed & 10 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{NGC 2632 DEC model hyperparameters.}
    \label{tab:hyperparameters_ngc_2632}
  \end{center}
\end{table}

\begin{table}[H]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \textbf{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \textbf{$\mu_{\delta}$ $(mas/yr^{-1})$} & \textbf{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -36.047 $\pm$ 0.110 & -12.917 $\pm$ 0.066 & 5.371 $\pm$ 0.003 & - \\
      Clusterix+TOPCAT & -36.154 $\pm$ 1.001 & -12.909 $\pm$ 0.806 & 5.327 $\pm$ 0.187 & 371 \\
      KMeans & -26.352 $\pm$ 20.562 & -15.828 $\pm$ 19.152 & 5.394 $\pm$ 0.696 & 629 \\
      DEC & -20.012 $\pm$ 20.657 & -14.742 $\pm$ 17.330 & 4.686 $\pm$ 0.855 & 894 \\
      \textbf{DEC (filtered)} & -21.571 $\pm$ 19.825 & -14.234 $\pm$ 16.388 & 4.719 $\pm$ 0.706 & 714 \\
    \end{tabular}
    \caption{NGC 2632 results.}
    \label{tab:results_ngc_2632}
  \end{center}
\end{table}

>>>>

@@

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \textbf{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \textbf{$\mu_{\delta}$ $(mas/yr^{-1})$} & \textbf{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr}\tablefootnote{Results have been taken from \protect\citeA[p.~25. Table A.3. Pleiades]{babusiaux2018gaia}} &
        19.997 $\pm$ 0.127 & -45.548 $\pm$ 0.101 & 7.364 $\pm$ 0.005 & 1326 \\
      Clusterix+TOPCAT & 19.98 $\pm$ 1.25 & -45.47 $\pm$ 1.48 & 7.33 $\pm$ 0.21 & 634 \\
      KMeans & 20.25 $\pm$ 35.16 & -38.01 $\pm$ 40.16 & 7.23 $\pm$ 2.35 & 1378 \\
      DEC & 23.67 $\pm$ 38.33 & -46.23 $\pm$ 44.54 & 8.04 $\pm$ 2.59 & 878 \\
      \textbf{DEC (filtered)} & 19.50 $\pm$ 8.59 & -44.23 $\pm$ 8.17 & 7.42 $\pm$ 0.1 & 438 \\
    \end{tabular}
    \caption{Melotte 22. The parameters shown are proper motion in right ascension and declination, parallax and number of stars with their respective deviations.}
    \label{tab:results_melotte_22}
  \end{center}
\end{table}

@@

\subsection{NGC 2516}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/pm_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/parallax_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/hr_diagram_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2516 Clusterix+TOPCAT characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_pm_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_parallax_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_hr_diagram_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2516 KMeans characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_pm_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_parallax_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_hr_diagram_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2516 DEC characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_pm_filtered_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_parallax_filtered_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_hr_diagram_filtered_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2516 DEC (filtered) characterization.}
\end{figure}

\vfill

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 8 \\
      Clustering Layer & $\left[ 50, 50, 60 \right]$ \\
      Kernel Initializer Seed & 2 \\
      Quantil Threshold & 0.15 \\
    \end{tabular}
    \caption{NGC 2516 DEC model hyperparameters.}
    \label{tab:hyperparameters_ngc_2516}
  \end{center}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \textbf{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \textbf{$\mu_{\delta}$ $(mas/yr^{-1})$} & \textbf{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -4.6579 $\pm$ 0.0075 & 11.1517 $\pm$ 0.0075 & 2.4118 $\pm$ 0.0006 & 1727 \\
      Clusterix+TOPCAT & -4.652 $\pm$ 0.523 & 11.203 $\pm$ 0.454 & 2.409 $\pm$ 0.127 & 638 \\
      KMeans & -4.344 $\pm$ 5.670 & 9.507 $\pm$ 7.546 & 2.268 $\pm$ 0.288 & 1542 \\
      DEC & -4.426 $\pm$ 6.529 & 9.952 $\pm$ 8.018 & 2.436 $\pm$ 0.358 & 1532 \\
      \textbf{DEC (filtered)} & -4.502 $\pm$ 4.46 & 10.114 $\pm$ 5.719 & 2.392 $\pm$ 0.135 & 1072 \\
    \end{tabular}
    \caption{NGC 2516 results.}
    \label{tab:results_ngc_2516}
  \end{center}
\end{table}

\vfill

@@

\begin{figure}[H]
  \vfil
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 Clusterix+TOPCAT characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 KMeans characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 DEC characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_pm_filtered_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_filtered_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_filtered_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 DEC (filtered) characterization.}
\end{figure}

\vfill

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 10 \\
      Clustering Layer & $\left[ 50, 50, 40 \right]$ \\
      Kernel Initializer Seed & 10 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{NGC 2632 DEC model hyperparameters.}
    \label{tab:hyperparameters_ngc_2632}
  \end{center}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \textbf{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \textbf{$\mu_{\delta}$ $(mas/yr^{-1})$} & \textbf{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -36.047 $\pm$ 0.110 & -12.917 $\pm$ 0.066 & 5.371 $\pm$ 0.003 & - \\
      Clusterix+TOPCAT & -36.154 $\pm$ 1.001 & -12.909 $\pm$ 0.806 & 5.327 $\pm$ 0.187 & 371 \\
      KMeans & -26.352 $\pm$ 20.562 & -15.828 $\pm$ 19.152 & 5.394 $\pm$ 0.696 & 629 \\
      DEC & -20.012 $\pm$ 20.657 & -14.742 $\pm$ 17.330 & 4.686 $\pm$ 0.855 & 894 \\
      \textbf{DEC (filtered)} & -21.571 $\pm$ 19.825 & -14.234 $\pm$ 16.388 & 4.719 $\pm$ 0.706 & 714 \\
    \end{tabular}
    \caption{NGC 2632 results.}
    \label{tab:results_ngc_2632}
  \end{center}
\end{table}

\vfill
